---
title: "Bad Plot vs. Good Plot"
author: "Kevin Candray"
date: "3/20/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro
```{r}
#loading the libs 
library(tidyverse)
library(ggplot2)
library(here)
library(dplyr)

```

# Loading the Data
```{r}
christmas_songs <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-12-24/christmas_songs.csv")
View(christmas_songs)
```

# Changing the Month number to the month name 
```{r}
#christmas_songs$month <- as.factor(christmas_songs$month) #change month from character to factor so we can rename levels
christmas_songs$month <- recode_factor(christmas_songs$month, #rename month levels to numbers
                             "1" = "January",
                             "2" = "February",
                             "3" = "March",
                             "4" = "April",
                             "5" = "May",
                             "6" = "June",
                             "7" = "July",
                             "8" = "August",
                             "9" = "September",
                             "10" = "October",
                             "11" = "November",
                             "12" = "December")
christmas_songs$month<- as.numeric(christmas_songs$month)
MCAG_Songs<- christmas_songs %>% filter(performer == 'Mariah Carey' | performer == 'Ariana Grande')
```

# Bad Plot  
This is a bad plot because the title does not fully explain what the graph is about. The labels of the x and y axis are confusing because it is unknown what the numbers mean. 1, 2, 3 could be apples, oranges, etc. The data itself is very convoluted because it is unknown what it's trying to say. Is 100 good or bad? is it a rank? what are the dots? many questions unanswered.
```{r}
MCAG_Songs %>% 
  ggplot(aes(x = month, # name x axis 
             y = week_position, # name y axis 
             color = performer))+
  geom_line()+
  geom_jitter()+
  labs(x= "month",
       y= "week position",
       title = "Mariah vs Ariana Xmas Music")
  ggsave(here("Week_7", "output","badplot.png"), width = 9, height = 8)
  
```
# Good Plot  
This a good plot because the title explains what the graph(s) are about. The x and y axis are properly labeled. The legend is in a better location, the data is cut into the different years. It is clear to see that Mariah charts higher on the Billboard Hot 100 more than Ariana. 
```{r}
MCAG_Songs %>% 
  ggplot(aes(x = month, # name x axis 
             y = week_position, # name y axis 
             color = performer))+
  geom_line(size=1.2)+
  geom_jitter(size=1)+
  labs(title = "Weekly Performer Position of X-Mas Music",
       x= "Time (months)", 
       y= "Week Position")+
  theme_bw() +
   scale_x_continuous(expand = c(0, .1),
                     breaks = seq(1, 3, 1),
                     labels = c("Jan.", "Jun.", "Dec.")) + #rename months
  scale_y_continuous(expand = c(0, 1)) +
  theme(legend.position = c(0.85, 0.15), #move legend into empty space
        legend.background = element_blank(), 
        plot.margin = margin(60, 60, 30, 30)) + #put margin around plot
  facet_wrap(~year) + #make one plot for each variable
  labs(y = "Billboard Hot 100 Week Position",
       x = "",
       color = "",
       title = "Weekly Position of Ariana Grande & Mariah Carey Christmas Music \n",
       caption = "Made by: Kevin Candray")+
  scale_color_manual(values = c("Ariana Grande" = "#26b575",
                                "Mariah Carey" = "#ff0000")) +
  theme(axis.title = element_text(size = 12))+
  ggsave(here("Week_7", "output","goodplot.png"), width = 9, height = 8)
```

